% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Abhijeet Anand} \hfill
\textsf{\small AbhijeetAnand@lbl.gov, https://abhi0395.github.io} \\[0.5ex]
Postdoctoral Scientist, Lawrence Berkeley National Lab, Berkeley, CA\\[0.5ex]

\cvheading{Positions}
\begin{list}{}{\cvlist}
\item
Sep'22 - Aug'25: Postdoctoral Scientist, Lawerence Berkeley National Lab (LBNL), Berkeley, CA, USA
\item
Aug'22: Bridge Postdoctoral Fellow, Max Planck Institute for Astrophysics, Garching, Germany
\item
Sep'18 - Jul'22: IMPRS PhD Fellow, Max Planck Institute for Astrophysics, Garching, Germany
\end{list}

\cvheading{Education}
\begin{list}{}{\cvlist}
\item
Sep 2018 - Jul 2022: PhD in Astrophysics, Ludwig Maximilian University - Max Planck Institute for Astrophysics (MPA), Germany.
    \subitem Thesis: \href{https://edoc.ub.uni-muenchen.de/30337/}{Probing cool and warm circumgalactic gas in galaxies and clusters with large spectroscopic and imaging surveys}
    \subitem Advisors: \href{https://www.mpa-garching.mpg.de/galaxyformation}{Prof. Dr. Guinevere Kauffmann} \& href{https://www.ita.uni-heidelberg.de/%7Ednelson/}{Dr. Dylan Nelson}
\item
Jul 2016 - Jul 2017: MS, Physics, Indian Institute of Science (IISc), Bangalore, India.
\item
Aug 2012 - June 2016: BSc (Research), Physics, Indian Institute of Science, Bangalore, India.
\end{list}

\cvheading{Selected publications}
\begin{list}{}{\cvlist}
\input{pubs_select}
\end{list}

\cvheading{Popular open-source software}
\begin{list}{}{\cvlist}

\item {\bf emcee} ---
    MCMC sampling in Python. Popular in astronomy;
    the paper has over 1000 citations.
    \url{emcee.readthedocs.io}

\item {\bf george} ---
    Blazingly fast Gaussian processes for regression. Implemented in C++ and
    Python bindings. Joint work with applied mathematicians at NYU.
    \url{george.readthedocs.io}

\item {\bf celerite} ---
    Scalable computations for Gaussian process regression for one-dimensional
    problems.
    \url{celerite.readthedocs.io}

\item {\bf corner.py} ---
    Simple corner plots (or scatterplot matrices) in Python.
    \url{corner.readthedocs.io}

\end{list}

%\cvheading{Honors}
%\begin{list}{}{\cvlist}
%\item Kavli Fellow, 2015.
%\item Sagan Postdoctoral Fellowship, 2015--present.
%\item James Arthur Graduate Fellowship, 2014.
%\item Horizon Fellowship in the Natural \& Physical Sciences, 2012.
%\item Henry M. MacCracken Fellowship, 2010.
%\item NSERC Undergraduate Summer Research Award, 2007.
%\end{list}

\end{document}
