% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}
\input{cvstyle}
\newcommand{\tex}[1]{#1}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Abhijeet Anand, PhD}\\[0.5ex]
Postdoctoral Scientist, Lawrence Berkeley National Lab, CA, USA\\[0.5ex]
\textsf{\small AbhijeetAnand@lbl.gov, \href{https://abhi0395.github.io/}{https://abhi0395.github.io/}}\\[0.5ex]

\subsection{Research Interests}
My research focuses on understanding the physical properties and kinematics of the circumgalactic medium (CGM) using quasar absorption lines. I am particularly interested in the interaction between gas flows and galaxy evolution across cosmic time. I also develop and apply innovative methods for analyzing large astronomical datasets, with a strong commitment to fostering diversity and inclusion within the scientific community.

\subsection{Positions}
\begin{list}{}{\cvlist}
\item Sep'22 - present: Postdoctoral Scientist, Lawrence Berkeley National Lab, Berkeley, CA, USA \\
\begin{itemize}
  \item \emph{Improved redshift estimation algorithms for DESI galaxies using spectroscopic data for cosmological and astrophysical studies.}
  \item \emph{Led cross-disciplinary projects involving data analysis, modeling, and interpretation of large astronomical datasets.}
\end{itemize}
%\item Aug'22: Bridge Postdoctoral Fellow, Max Planck Institute for Astrophysics, Garching, Germany
\item Sep'18 - Jul'22: IMPRS PhD Fellow, Max Planck Institute for Astrophysics, Garching, Germany
\begin{itemize}
\item \emph{Conducted extensive studies on the gas distribution in the circumgalactic and intracluster medium using data from SDSS and DESI.}
\item \emph{Developed the quasar absorber finder, \href{https://github.com/abhi0395/qsoabsfind}{qsoabsfind}, a tool used for detecting and analyzing metal absorbers in quasar spectra.}
\end{itemize}
\item Sep'17 - Jul'18: UGC - JRF\footnote{University Grants Commission, Govt. of India - Junior Research Fellowship}, National Institute of Advanced Studies, Bangalore, India
\end{list}

\subsection{Education}
\begin{list}{}{\cvlist}
  \item Sep 2018 - Jul 2022: PhD in Astrophysics, Ludwig Maximilian University - Max Planck Institute for Astrophysics (MPA), Germany.
\begin{itemize}
    \item Thesis: \href{https://edoc.ub.uni-muenchen.de/30337/}{Probing cool and warm circumgalactic gas in galaxies and clusters with large spectroscopic and imaging surveys}
    \item Advisors: \href{https://www.mpa-garching.mpg.de/galaxyformation}{Prof. Dr. Guinevere Kauffmann} \& \href{https://www.ita.uni-heidelberg.de/~dnelson/}{Dr. Dylan Nelson}
\end{itemize}

\item Jul 2016 - Jul 2017: MS, Physics, Indian Institute of Science (IISc), Bangalore, India.
\begin{itemize}
    \item Thesis: \href{https://raw.githubusercontent.com/abhi0395/mycv/main/files/MS_thesis.pdf}{A sensitive search for HI 21 cm emission from super disks in radio galaxies}
    \item Advisor: \href{http://www.physics.iisc.ernet.in/%7Enroy/}{Prof. Nirupam Roy}
  \end{itemize}
\item Aug 2012 - June 2016: BSc (Research), Physics, Indian Institute of Science, Bangalore, India.
\begin{itemize}
    \item Thesis: \href{https://raw.githubusercontent.com/abhi0395/mycv/main/files/BS_thesis.pdf}{Sources of Continuum Opacity in Hydrogen deficient stars}
    \item Advisors: \href{https://www.iiap.res.in/?q=user/29}{Prof. Gajendra Pandey}, \href{https://www.iiap.res.in/}{Indian Institute of Astrophysics (IIA)}
  \end{itemize}
\end{list}

%\subsection{Research Interest}
%\begin{itemize}
%    \item Understanding gas in flows in galaxy halo (aka circumgalactic medium) using quasar absorption lines and its connection to galaxy formation and evolution
%    \item Developing new tools to fit and analyze astronomical spectra coming from large spectrscopic surveys
%\end{itemize}

\ifdefined\withpubs
  \subsection{Publications}
  \input{pubs_summary}

  \subsubsection{Refereed publications}
  \begin{list}{}{\cvlist}
    \input{pubs_ref}
  \end{list}

  \subsubsection{Preprints \& white papers}
  \begin{list}{}{\cvlist}
    \input{pubs_unref}
  \end{list}
\fi

\subsection{Selected visits, talks and conferences}
$^i$\emph{Invited Talks}, $^c$\emph{Contributed Talks}, $^s$\emph{Schools \& Workshops}
\begin{list}{}{\cvlist}
\item $^c$ Jul 2024:  \emph{DESI Collaboration Summer Meeting}, Marseille, France,   Jul 9 - Jul 12, 2024 (\textit{Virtual talk}).
\item $^i$ Feb 2024:  \emph{Extragalactic Seminar}, MPA Garching, Germany, Feb 29, 2024 (\textit{Talk}).
\item $^i$ Feb 2024:  \emph{Cosmology Seminar}, MPA Garching, Germany, Feb 27, 2024 (\textit{Talk}).
    %\item $^i$ Aug 2023:  \emph{DESI Data Systems and Management Meeting}, Oct 31, 2023 (\textit{Virtual Talk}).
%\item $^i$ Aug 2023:  \emph{DESI Data Systems and Management Meeting}, Aug 29, 2023 (\textit{Virtual Talk}).
\item $^c$ Dec 2023:  \emph{DESI Collaboration Winter Meeting}, Kona, Hawaii, Dec 11 - Dec 14, 2023 (\textit{Virtual talk}).
\item $^c$ Jul 2023:  \emph{DESI Collaboration Summer Meeting}, Durham, UK, Jul 17 - Jul 21, 2023 (\textit{Talk}).
\item $^c$ Mar 2023:  \emph{DESI Absorber Science Workshop}, Mar 28, 2023 (\textit{ Virtual Talk}).
\item $^c$ Dec 2022:  \emph{DESI Collaboration Winter Meeting}, Cancun, Mexico, 5-9 Dec, 2022 (\textit{Talk}).
%\item $^c$ Sep 2022:  \emph{\href{https://sites.google.com/unimib.it/gas2022/home}{What matter(s) around galaxies 2022}}, Champoluc, Italy, 12-16 Sep, 2022 (\textit{Virtual}).
\item $^c$ May 2022:  \emph{\href{https://indico.ph.tum.de/event/7018/}{Gas Flows around Galaxies}}, MPA, Garching, 24 May, 2022 (\textit{Talk}).
\item $^c$ Apr 2022:  \emph{\href{https://www.stsci.edu/contents/events/stsci/2022/april/galaxy-clusters-2022-challenging-our-cosmological-perspectives}{Galaxy Clusters 2022}}, STScI 25-29 Apr, 2022 (\textit{e-Poster}).
\item $^i$ Mar 2022:  \emph{\href{https://zah.uni-heidelberg.de/research-groups\#c2659}{Computational Galaxy Formation and Evolution Group}}, ZAH/ITA, University of Heidelberg, 14-16 Mar, 2022 (\textit{Visitor}).
\item $^i$ Feb 2022:  \emph{High Energy Group Seminar}, MPE Garching, 15 Feb, 2022 (\textit{Virtual}).
\item $^i$ Feb 2022:  \emph{DESI Group Seminar}, Berkeley Lab, 1 Feb, 2022 (\textit{Virtual}).
\item $^i$ Dec 2021:  \emph{\href{https://pweb.cfa.harvard.edu/calendar/event/9298}{Galaxies \& Cosmology Seminar}}, CfA Harvard, 13 Dec, 2021 (\textit{Virtual}).
\item $^i$ Sep 2021:  \textit{STARs lab}, Arizona State University, 24 Sep, 2021 (\textit{Virtual}).

\item $^c$ Nov 2021:  \emph{\href{https://www.bilibili.com/video/BV1nv411M7w3}{e-Poster \& talk}}, \emph{\href{https://kiaa.pku.edu.cn/KooGig_junior21/Home.htm}{KooGiG-Junior'21}}, KIAA, Peking University, 1-5 Nov, 2021 (\textit{Virtual}).

\item $^c$ Sep 2021:  \emph{\href{https://ag2021.astronomische-gesellschaft.de/view_splinter.php?session=Stars}{German Astronomical Society Meeting 2021}}, 16 Sep, 2021 (\textit{Virtual})
\item $^c$ Aug 2021:  \emph{\href{https://jhu2021.sdss.org/}{SDSS-IV Collaboration Meeting 2021}}, 12 Aug, 2021 (\textit{Virtual + e-poster})
\item $^s$ Jul 2021:  \emph{MIAPP Workshop: High-Energy Plasma Physics Phenomena in Astrophysics}, MIAPP, Garching, Jul 19 - 30, 2021 (\textit{Virtual participant}).

\item $^c$ Jun 2021:  \emph{MPA Galaxy Group Retreat}, Fraueninsel, Chiemsee, 14-17 June, 2021 (\textit{Talk}).
\item $^s$ Jan 2021:  \emph{Fundamental of Gaseous Halos}, KITP, UCSB, 11 Jan - 5 Mar, 2021 (\textit{Virtual participant}).
\item $^c$ Oct 2020:  \emph{Galaxy Introductory Symposium}, MPA, Garching, 27 Oct, 2020 (\textit{Virtual}).
\item $^c$ Oct 2020:  \emph{Institute Seminar}, MPA, Garching, 26 Oct, 2020 (\textit{Virtual}).

\item $^c$ Oct 2019:  \emph{\href{https://wwwmpa.mpa-garching.mpg.de/conf/berlincgm2019/}{CGM 2019: CGM Conference}}, Berlin, 3 Oct - 5 Oct 2019 (\textit{Participation}).
\item $^s$ Aug 2019:  \emph{Summer School: Galaxy Formation}, AKSS, Spetses, 28 Aug - 5 Sept 2019.
\item $^s$ Nov 2018:  \emph{Python for HPC}, attended at MPCDF, Garching, 20-21 Nov 2018.
\end{list}

 \subsubsection{Observing experience}
  \begin{list}{}{\cvlist}
  \item Jul 2024: Support Observing Scientist for DESI, Kitt Peak National Observatory, Jul 2-5, 2024 (four nights).
  \end{list}


\subsection{Mentoring}
\begin{list}{}{\cvlist}
\item Joanne Tan (MPA Garching PhD) (CGM absorbers in TNG-100), 2024-present
\item Corey Dodeson (UC Berkeley UG) (short-term reading project on CGM), 2023
\item Dylan Green (UC Irvine PhD) (as part of DESI mentorship program), 2023
\end{list}

\subsection{Honors \& Awards}
\begin{list}{}{\cvlist}
  \item DESI Early Career Travel Grant (USD 4000).
  \item DESI Postdoc Fellow, 2022--2025.
  \item IMPRS PhD Fellowship, 2018--2022.
  \item UGC - Junior Research Fellowship, 2017-2018 (INR 390,000).
  \item DST\footnote{Department of Science \& Technology, Govt. of India} - Higher Studies Scholarship, 2012-2017.

\end{list}

\subsection{Computer skills}
\begin{list}{}{\cvlist}
\begin{itemize}
\item[] Language/Packages ---
    python, numpy, matplotlib, scipy, astropy
\item[] OS/Tools --- Linux, Mac, \LaTeX, bash scripting, jupyter notebooks, slurm manager, git
\end{itemize}
\begin{itemize}
\item[] Member \& contributor (github repo) ---
    \begin{itemize}
        \item[] \href{https://github.com/abhi0395/qsoabsfind}{qsoabsfind}: QSO metal absorber finder (\textit{Developer}).
      \item[] \href{https://github.com/desihub/redrock}{redrock}: Redshift fitting for spectroperfectionism (\textit{Contributor}).
      \item[] \href{https://github.com/desihub}{desihub}: Public code associated with DESI (\textit{Contributor}).
      
  \end{itemize}
\end{list}

% \ifdefined\withpubs
%     \newpage
% \fi

\subsection{Professional service \& activities}
\begin{list}{}{\cvlist}
    \item Peer reviewer ---
    \href{https://en.wikipedia.org/wiki/Astronomy_%26_Astrophysics}{A\&A}
    , \href{https://en.wikipedia.org/wiki/The_Astrophysical_Journal}{ApJ}, Internal Reviewer for DESI collaboration papers
    \item Collaboration ---
        \href{https://www.desi.lbl.gov/}{Dark Energy Survey Instrument (DESI)}, NANCY
    \item Organizer ---
        \href{https://inpa.lbl.gov/events/}{INPA Weekly Seminar}, Physics Division, LBNL
    \item Active mentor in DESI mentorship program and member of DESI DEI committee.
    \item Appeared in \href{https://www.youtube.com/watch?v=WmA_PnYLeCg}{podcast} to discuss my astronomy journey and how people from small cities can become a successful astronomer.
    \item My papers (\href{https://www.mpa-garching.mpg.de/964620/hl202107}{I}, \href{https://www.mpa-garching.mpg.de/1066558/hl202211?c=27981}{II}) featured in monthly research highlight of MPA and appeared on \href{https://astrobites.org/2021/05/06/cool-metal-gas-search-thanks-it-was-automated/}{astrobites}.
    \item Gave \href{https://theinterviewportal.com/2020/03/13/astrophysicist-interview-8/}{interview} to \href{https://theinterviewportal.com/}{The Interview Portal} to help Indian college students plan their careers.
    \item Member of Local organizing Committee of VII\textsuperscript{th} IMPRS Student Symposium, 4-5 Apr, 2019.
  \item Served as online physics tutor at E-acharya (more than 20 students)\footnote{an initiative to help poor students in sub-urban and rural areas of Bihar, India.} from June 2017 - Aug 2018.
    \item Advanced Physics tutor at Chegg India from Jul 2016 - Dec 2017. Solving advance physics problems and clearing doubts of students from all over the world.
  \item Organized and coordinated scientific and technical workshops ($\sim$ 150 participants) in \emph{Pravega}\footnote{Annual Science Festival of IISc}, in Jan'14.
    \item Conducted experiments and demonstrations for open day celebration at IISc during my undergraduate.
\end{list}

\end{document}
