\documentclass[a4paper,10pt]{article}
\usepackage{amssymb}
\usepackage[left=0.775in, right=0.775in, top=0.75in, bottom=0.8in]{geometry}
\usepackage{enumitem, hyperref, titlesec, amsmath, color, changepage}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}
\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}

\definecolor{sectionblue}{RGB}{2,2,100}

\titleformat{\section}
  {\color{sectionblue}\normalfont\Large\bfseries}
  {}{0em}{}[\titlerule]

\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{itemsep=2pt, topsep=4pt}

\begin{document}

\begin{center}
    {\huge \textbf{Abhijeet Anand, PhD}} \\
    {\normalsize \vspace{2mm}
    \textbf{Independent Fellow, Inter-University Centre for Astronomy and Astrophysics (IUCAA)}}
    \vspace{-1mm}
    \begin{center}
    \normalfont
    \href{mailto:abhijeetanand2011@gmail.com}{abhijeetanand2011@gmail.com} \quad | \quad
    +91 88615 59447 \quad | \quad Pune, India \quad | \quad
    \href{https://www.linkedin.com/in/abhijeet-anand-iisc}{LinkedIn} \quad | \quad
    \href{https://scholar.google.com/citations?hl=en&user=MfOuq1IAAAAJ}{Scholar} \quad | \quad
    \href{https://github.com/abhi0395}{GitHub}
    \end{center}
\end{center}


\vspace*{-1.5mm}
\begin{center}
\textit{Computational Physicist and Data Scientist with 7+ years of experience developing, maintaining, and improving open-source scientific software and large-scale analysis pipelines for astronomy. Strong background in scientific Python ecosystem, including statistical validation, workflow automation, collaborative Git/GitHub based software development, automated testing and CI/CD workflows, documentation, versioned software releases. Experience in communicating technical results across multidisciplinary teams.}
\end{center}

\vspace*{-2mm}

\section*{Work Experience}

\textcolor{sectionblue}{\textbf{Independent Postdoctoral Fellow}} \hfill
\textcolor{sectionblue}{\textit{IUCAA, Pune}} \hfill
\textcolor{sectionblue}{\textit{Dec 2025 -- Present}}\\
\textcolor{sectionblue}{\textbf{Affiliate Scientist}} \hfill
\textcolor{sectionblue}{\textit{Lawrence Berkeley National Laboratory, USA}} \hfill
\textcolor{sectionblue}{\textit{Feb 2026 -- Present}}

\vspace{1.5mm}
\begin{adjustwidth}{1em}{0pt}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Lead end-to-end data analysis projects, from preparing noisy datasets and building detection models to validating results and delivering community data products.
    \item Develop and maintain Python pipelines for one-dimensional sequential data, including transformation, signal processing, classification, and uncertainty analysis.
    \item Apply supervised and unsupervised methods, including regression, classification, PCA, NMF, resampling, and matched-filter techniques.
    \item Mentor students, coordinate project timelines, and promote reproducible and maintainable coding practices.
\end{itemize}
\end{adjustwidth}

\vspace{1.5mm}

\textcolor{sectionblue}{\textbf{Postdoctoral Fellow}} \hfill
\textcolor{sectionblue}{\textit{Lawrence Berkeley National Laboratory, USA}} \hfill
\textcolor{sectionblue}{\textit{Sep 2022 -- Oct 2025}}

\vspace{1.5mm}
\begin{adjustwidth}{1em}{0pt}

\textcolor{sectionblue}{\textbf{\underline{Data Science and Software Development}}}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Developed and validated analytical models for large scientific datasets, including a hybrid PCA-based method that reduced major classification failures by approximately \textbf{30\%}.
    % \item Built scalable Python workflows for data cleaning, transformation, feature extraction, model evaluation, and quality control.
    \item Defined and tracked analysis-quality metrics, including failure rates, detection reliability, completeness, and validation statistics, to guide model and pipeline improvements.
    \item Contributed to open-source software through feature development, debugging, code review, automated testing, documentation, and versioned releases.
    \item Managed collaborative development through GitHub, including issue tracking, pull requests, CI/CD workflows, and tagged releases.
\end{itemize}

\vspace{0.5mm}
\textcolor{sectionblue}{\textbf{\underline{Large-Scale Computing and Project Leadership}}}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Supported daily production workflows on \href{https://www.nersc.gov/}{NERSC} systems using Python, Slurm, parallel processing, and automated validation.
    \item Investigated workflow failures, identified root causes, and coordinated fixes across data, software, and computing teams.
    \item Led analytical and software workstreams from problem definition through implementation, testing, delivery, and communication of results.
    \item Mentored junior researchers and coordinated technical priorities, milestones, and project deliverables.
\end{itemize}
\end{adjustwidth}

\vspace{2mm}

\textcolor{sectionblue}{\textbf{PhD Research Fellow}} \hfill
\textcolor{sectionblue}{\textit{Max Planck Institute for Astrophysics, Germany}} \hfill
\textcolor{sectionblue}{\textit{Sep 2018 -- Jul 2022}}

\vspace{1.5mm}
\begin{adjustwidth}{1em}{0pt}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Developed a Python-based signal-detection tool for identifying weak features in noisy one-dimensional data.
    \item Built parallel analysis workflows that achieved over 95\% detection reliability and reduced runtime from weeks to hours.
    \item Performed large-scale statistical validation using resampling, completeness testing, uncertainty analysis, and reproducible pipelines.
    \item Led projects from method design and implementation through validation, publication, and release of reusable data products.
\end{itemize}
\end{adjustwidth}

\vspace*{-1mm}

\section*{Selected Open-Source Software}
\begin{adjustwidth}{1em}{0pt}
\begin{itemize}[leftmargin=*, itemsep=3pt]
    \item \textbf{\href{https://github.com/abhi0395/qsoabsfind}{qsoabsfind}} --- Developer and maintainer of a scalable Python package for signal detection, classification, and measurement in noisy sequential data.
    \item \textbf{\href{https://github.com/abhi0395/nmfqsofit}{nmfqsofit}} --- Developer and maintainer of a Python package for data reconstruction and feature modeling using non-negative matrix factorization.
    \item \textbf{\href{https://github.com/desihub/redrock}{redrock}} and \textbf{\href{https://github.com/desihub/desispec}{desispec}} --- Contributor to large-scale data-processing and model-fitting software used by an international scientific collaboration.
\end{itemize}
\end{adjustwidth}

\vspace*{-2mm}

\section*{Technical Skills}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{p{3.4cm} p{12.5cm}}
    \textbf{Data Science \& ML} & Python, NumPy, SciPy, pandas, scikit-learn, regression, classification, clustering, PCA, NMF, model validation \\
    \textbf{Statistics \& Signals} & Statistical inference, probability, hypothesis testing, bootstrapping, uncertainty analysis, one-dimensional sequential data, convolution, matched filtering, feature detection, noise modeling \\
    \textbf{Data Engineering} & Basic SQL for data access, data cleaning, data transformation, ETL-style workflows, structured and unstructured data, FITS, HDF5, parallel I/O \\
    \textbf{Software Development} & Git, GitHub, code review, unit testing (\textit{pytest}), GitHub Actions, CI/CD, automated validation, modular package design, Sphinx documentation \\
    \textbf{Large-Scale Computing} & Linux, NERSC Perlmutter, Slurm, multiprocessing, MPI, performance debugging, Jupyter \\
    \textbf{Leadership} & Project ownership, mentorship, cross-team collaboration, technical communication, project coordination
\end{tabular}
\renewcommand{\arraystretch}{1.0}

\vspace*{-2mm}

\section*{Selected Professional Activities}
\begin{adjustwidth}{1em}{0pt}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Awarded Builder status, given to approximately 10\% of collaboration members, for contributions to survey operations and data systems in one international project.
    \item Core member of the institute Computing Facilities Committee, contributing to research-computing planning and user support.
    \item Awarded a three-year Max Planck India Mobility Grant (2026--2029), given by Max Planck Society of Germany.
    \item Author of 48 publications, including 5 first-author papers, with more than 6000 citations.
    \item Referee for \textit{Nature Astronomy}, \textit{Astronomy \& Astrophysics}, and \textit{The Astrophysical Journal}.
\end{itemize}
\end{adjustwidth}

\vspace*{-2mm}

\section*{Education}

\textcolor{sectionblue}{\textbf{PhD in Astrophysics}} \hfill
\textit{Max Planck Institute for Astrophysics, Garching, Germany} \hfill
\textit{Sep 2018 -- Jul 2022}\\
\vspace{-1.5mm}
\textcolor{sectionblue}{\textbf{BS--MS in Physics}} \hfill
\textit{Indian Institute of Science (IISc), Bangalore, India} \hfill
\textit{Aug 2012 -- Jun 2017}

\end{document}
